Automatically generated NE tagged corpora for English and Hungarian

### 2012-04-26 paper/engNERwiki.tex
Acknowledgements.
NLTK citation modified.

Our goal is to create a large NE annotated corpus, automatically generated from Wikipedia articles. We follow a similar path to Nothman et al.~\shortcite{Nothman:08}, who broke down the process into four steps:

\begin{enumerate}
\item Classify all articles into entity classes.
\item Split Wikipedia articles into sentences.
\item Label NEs according to link targets.
\item Select sentences for inclusion in the corpus.
\end{enumerate}

%Subsectionöket valahogy ez alapján kéne.

In this section, we describe how these steps were implemented. While the approach in essence is language-independent, the exact details XXX have to be accomodated to the target language. 
%Ez utóbbi mondat mit jelent?

%This section explains the general idea and its execution for English; the next section describes how the idea is adapted to Hungarian.

The English corpus is based on the Wikipedia snapshot as of January 15, 2011. The XML files were parsed by the mwlib parser\footnote{http://code.pediapress.com}. The raw text was tokenized by a modified version of the Punkt sentence and word tokenizers \cite{Kiss:06} in NLTK. 
%\cite{Loper:02}. 
Lemmatization was performed using the Wordnet Lemmatizer, also in NLTK. Part-of-speech tagging was performed by HunPos \cite{Halacsy:07}.
%The words were lemmatized with the Wordnet Lemmatizer, also in NLTK, and POS tagged with \texttt{HunPos} \cite{Halacsy:07}.

%Chunking was performed with HunChunk (CITE). Experiments have shown that HunPos obtains STAT f-score on the Brown corpus; HunChunk performs at around STAT, CITE?.

@@

@@

\subsubsection{Sentence Filtering}

@@

@@

%\section*{Acknowledgments}

%The authors are grateful to Attila Zséder and Gábor Recski for their respective work on Wikipedia parsing and {\tt hunner}.
% + CE(A?)SAR

@@

\bibitem[\protect\citename{Loper and Bird}2002]{Loper:02}
Edward Loper, Steven Bird.
\newblock 2002.
\newblock NLTK: the Natural Language Toolkit. 
\newblock In: {\em Proceedings of the ACL-02 Workshop on Effective tools and methodologies for teaching natural language processing and computational linguistics}, Volume 1, pages 63--70.

>>>>

Our goal is to create a large NE annotated corpus, automatically generated from Wikipedia articles. We follow a similar path to Nothman et al.~\shortcite{Nothman:08}, and we broke down the process into four steps:

\begin{enumerate}
\item Classify Wikipedia articles into entity classes.
\item Parse Wikipedia and split articles into sentences.
\item Label NEs according to link targets.
\item Select sentences for inclusion in the corpus.
\end{enumerate}

In this section, we describe how these steps were implemented. This section explains the general approach and its execution for English; the next section describes how the idea is adapted to Hungarian.

%While the approach in essence is language-independent, the exact details have to be accomodated to the target language.

@@

The English corpus is based on the Wikipedia snapshot as of January 15, 2011. The XML files were parsed by the mwlib parser\footnote{http://code.pediapress.com}. The raw text was tokenized by a modified version of the Punkt sentence and word tokenizers \cite{Kiss:06}. Lemmatization was performed using the Wordnet Lemmatizer in NLTK \cite{Bird:09}. Part-of-speech tagging was performed by HunPos \cite{Halacsy:07}.

%Chunking was performed by HunChunk (CITE). Experiments have shown that HunPos obtains STAT f-score on the Brown corpus; HunChunk performs at around STAT, CITE?.

@@

\subsection{Sentence Filtering}

@@

% TODO: <NE>-<random kisbetűs szó> => nem NE (magyar). Lásd: "a tű nélküli mezoterápia alapja a <Nobel, PER>-díjas"

@@

\section*{Acknowledgments}

% TODO: the corpora will be published in the META-SHARE repository.
This research was supported by the CESAR project under the ICT Policy Support Programme (grant 271022). The authors are grateful to Attila Zséder for his work on Wikipedia parsing.

@@

\bibitem[\protect\citename{Bird et al.}2009]{Bird:09}
Steven Bird, Ewan Klein, Edward Loper.
\newblock 2009.
\newblock {\em Natural Language Processing with Python}.
\newblock O'Reilly Media Inc.
